Does motif participation provide unique information about species risk of extinction?

### 2021-09-29 manuscript/reorder_main_text.tex

        We test whether networks with the the same size and connectance have more similar motif profiles using a PERMANOVA~\citep{Anderson2001} (Appendix \emph{3.2}). 
        To identify correlations between size, connectance, and participation in particular motifs, we fit an additional set of four LMMs:

@@

        As well as species-specific probabilities of persistence, motifs may provide information about the overall probability of any species going extinct (since they incorporate information on indirect effects).
        To test whether networks with similar motif profiles tend to have similar mean persistences among consumers, we fit a PERMANOVA relating Bray-Curtis dissimilarity in motif profiles to the mean persistence of all consumers in a network (averaged across all levels of disturbance to basal resources).
        To identify the relationships between particular motifs and network mean persistence, we fit a set of four LMMs (one per motif):

                \begin{equation}
                \Psi_{ik} \approx \Bar{\rho}_{i} + \pi_{disturbed_k} + \Bar{\rho}_{i}\pi_{disturbed_k} +
                S_{i}C_{i} ,
                \label{netpropeq}
            \end{equation}

@@

        Different scales of network structure (e.g., local and meso-scale) are not independent. 
        To test whether networks with the the same size and connectance have more similar motif profiles using a PERMANOVA~\citep{Anderson2001} of Bray-Curtis dissimilarity among motif profiles against network size, connectance, and their interaction. 
        In addition, we identify correlations between size, connectance, and particular motifs using a set of four LMMs:

        \begin{equation}
            \rho_{i} \approx S_{i} + C_{i} + S_{i}C_{i}
        \end{equation}
        where all symbols are as in equation~\ref{propreq}.

    \subsubsection*{5) Persistence and network properties}

>>>>

        We test whether networks with the the same size and connectance have more similar motif profiles using a PERMANOVA~\citep{Anderson2001} (Appendix \emph{3.2}). 
        To identify correlations between size, connectance, and participation in particular motifs, we fit a set of four linear models (LMs):

@@

        As well as species-specific probabilities of persistence, motifs may provide information about the overall probability of any species going extinct (since they incorporate information on indirect effects).
        We tested whether networks with similar motif profiles tend to have similar mean persistences among consumers using a PERMANOVA (Appendix \emph{S3.3}.
        To identify the relationships between particular motifs and network mean persistence, we fit a set of four LMs (one per motif):

            \begin{equation}
                \Psi_{ik} \approx \Bar{\rho}_{i} + \pi_{disturbed_k} + \Bar{\rho}_{i}\pi_{disturbed_k},
                \label{netpropeq}
            \end{equation}

@@

        Different scales of network structure (e.g., local and meso-scale) are not independent. 
        To test whether networks with the the same size and connectance have more similar motif profiles using a PERMANOVA~\citep{Anderson2001} of Bray-Curtis dissimilarity among motif profiles against network size, connectance, and their interaction (Appendix \emph{S3.4}). 
        In addition, we identify correlations between size, connectance, and particular motifs using a set of four LMs:

        \begin{equation}
            \Bar{\rho_{i}} \approx \Sigma_{i} + \zeta_{i} + \Sigma_{i}\zeta_{i}
        \end{equation}
        where all symbols are as in equations~\ref{propreq} and~\ref{netpropeq}.

    \subsubsection*{5) Persistence and network properties}
        $\Sigma$ and $\zeta$ for fixed effects, SC for random.
